Results from the deep learning challenge associated with the 3MD4040 lecture on plankton classification

### 2022-08-16 Report/paper.tex
rm useless figure

The cross entropy loss for the training set and the F1 score for the validation split are shown on figure~\ref{fig:sample_submission_losses}. The confusion matrices of the best parameters for the four trained networks are shown on figure~\ref{fig:sample_submission_confusion_matrix}. For every run, the best parameters are the one with the largest validation F1 score.

\begin{figure}[!htbp]
	\caption{\label{fig:sample_submission_losses} The cross entropy loss on the training set and the macro F1 score on the validation fold for the four trained models.}
\end{figure}

>>>>

The cross entropy loss for the training and validation sets and the F1 score for the validation split are shown on figure~\ref{fig:sample_submission_train_CE}-\ref{fig:sample_submission_test_F1}. The confusion matrices of the best parameters for the four trained networks are shown on figure~\ref{fig:sample_submission_confusion_matrix}. For every run, the best parameters are the one with the largest validation F1 score.

\begin{figure}
	\centering
	\def\svgwidth{0.5\columnwidth}
	\input{figs/metrics_train_CE.pdf_tex}
	\caption{\label{fig:sample_submission_train_CE}Averaged train cross entropy.Each were allowed to run for 48 hours. Light blue is resnet18, dark blue is resnet152, orange is regnety\_16 and red is efficientnet b3. }
\end{figure}
\begin{figure}
	\centering
	\def\svgwidth{0.5\columnwidth}
	\input{figs/metrics_test_CE.pdf_tex}
	\caption{\label{fig:sample_submission_valid_CE}Averaged cross entropy on the validation fold.Each were allowed to run for 48 hours. Light blue is resnet18, dark blue is resnet152, orange is regnety\_16 and red is efficientnet b3. }
\end{figure}

\begin{figure}
	\centering
	\def\svgwidth{0.5\columnwidth}
	\input{figs/metrics_fix_test_F1.pdf_tex}
	\caption{\label{fig:sample_submission_test_F1}Macro F1 scores on the validation fold for the four trained sample submissions. Each were allowed to run for 48 hours. Light blue is resnet18, dark blue is resnet152, orange is regnety\_16 and red is efficientnet b3. }
\end{figure}
